---
title: "Causal Inference"
author: "Ali Jaffri"
date: "2023-12-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load the dataset

```{r}
data_frame <- read.csv("njmin3.csv")
```

# Summarize the Dataset
```{r}

summary(data_frame)

```



# Taking into account missing values and replacing the missing values with the mean of the series


```{r}
data_frame$fte <- ifelse(is.na(data_frame$fte),
                         ave(data_frame$fte,FUN = function(x) mean(x,na.rm =TRUE)),data_frame$fte)
```

```{r}
summary(data_frame)
```

```{r}
data_frame$demp <- ifelse(is.na(data_frame$demp),
                         ave(data_frame$demp,FUN = function(x) mean(x,na.rm =TRUE)),data_frame$demp)
```



```{r}
summary(data_frame)
```


# Create the First Regression Model

```{r}

model1<- lm(fte ~ NJ+ POST_APRIL92+NJ_POST_APRIL92,data = data_frame)

summary(model1)

```

# The Second Regression
# Create a Base line for comparison so in this model we have excluded roys as an indepedent varaible as it will serve as a baseline

```{r}
model2<- lm(fte ~ NJ+ POST_APRIL92+NJ_POST_APRIL92+
              bk+kfc+wendys,data = data_frame)

summary(model2)
```

# Create the last regression

```{r}
model3<- lm(fte ~ NJ+ POST_APRIL92+NJ_POST_APRIL92+
              bk+kfc+wendys+co_owned+centralj+southj,data = data_frame)

summary(model3)
```
# Visualizing Results

```{r}
install.packages("stargazer")
```
```{r}
library(stargazer)

stargazer(model1,model2,model3,
          type = 'text',
          title = 'Impact of Minimum Wage on Employment',
          no.space = TRUE,
          keep.stat = 'n',
          digits = 2
          )
```




# Second Case study for practice

```{r}
install.packages('haven')
library(haven)

```
# Read the data from stata extension file  we need haven package in R


```{r}
data_set_eitc <- read_dta('eitc.dta')
```


# Create dummy varaibles
```{r}
data_set_eitc$post93 <-ifelse(data_set_eitc$year>1993,1,0)
data_set_eitc$mom <-ifelse(data_set_eitc$children>0,1,0)
data_set_eitc$mompost93 <- data_set_eitc$post93 *data_set_eitc$mom
```


# First Logistic Regression as our dependent variable is binary

```{r}
model1_log <-glm(work~post93+mom+mompost93,family = 'binomial',data = data_set_eitc)

summary(model1_log)

  
```
# Second Logistic Regression

```{r}
model2_log <-glm(work~post93+mom+mompost93
                   +nonwhite+ed+age+unearn
                   ,family = 'binomial',data = data_set_eitc)

summary(model2_log)
```
# Visualizing the Regression Results

```{r}
install.packages('stargazer')
library(stargazer)

```

```{r}
stargazer(model1_log,model2_log,
          type = 'text',
          align = TRUE,
          covariate.labels = c('After 1993','Is Mom',
          'Is Mom After 1993','Hispanic or White',
          'Years of Education','Age','Unearned Income'),
          
          digits = 2,
          no.space = TRUE
          )


```
#  Create Placebo Variables to perform placebo experiment 

```{r}

data_set_eitc$post92 <-ifelse(data_set_eitc$year>1992,1,0)
data_set_eitc$mompost92 <- data_set_eitc$post92 *data_set_eitc$mom

```

# create a placebo subset

```{r}

data_set_eitc_placebo <-subset(data_set_eitc,data_set_eitc$year<1994)

```

# Create Logistic Regression for Placebo Experiment

```{r}
model_placebo <-glm(work~post92+mom+mompost92+age+ed,family = 'binomial',data = data_set_eitc_placebo)

summary(model_placebo)
```


